High-resolution ALMA observations of V4046\,Sgr: a circumbinary disc with a thin ring

### 2020-11-19 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

Repeating the optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.86$\pm$0.02\,$\degr$, with an inclination of 33.92$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars. We see that both Ring13 and Ring24 both share a very similar orientation and centre, given the errors, and both are offset from the star. %Even though all orientation parameters for Ring13 and Ring24 are consistent within the errors, 
Perhaps due to the joint effect of all these small differences, we can see that there are some hints for a different orientation, as summarised in Fig.~\ref{fig:polarring}, .

@@

Assuming a three dimensional model in a cylindrical reference frame with coordinates ($r$, $\theta$, $z$), the gas density ($\rho_{\mathrm{gas}}$) distribution follows
\begin{equation}
  \rho_{\mathrm{gas}}(r,z) =\frac{\Sigma(r) \,\delta(r)}{\sqrt{2\pi} \, H(r)} \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{H(r)}\right)^2\right],
\end{equation}
where $\delta(r)$ parameterises the density drops in the gaps and cavities, $H(r)$ is the scale height profile and $\Sigma(r)$ is the surface density profile. $\Sigma(r)$ is defined by
\begin{equation}
  \Sigma(r) = \Sigma_\mathrm{c} \left(\frac{r}{R_\mathrm{c}}\right)^{-\gamma}  \, \mathrm{exp}\left[-\left(\frac{r}{R_\mathrm{c}}\right)^{2-\gamma}\right],
\end{equation}
where $R_c$ is a characteristic radius and $\gamma$ is the surface density gradient. A fixed $\gamma$ = 1 is used as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.

@@

Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a large inner cavity and scaling factors that account for the larger gap between the rings. For the inner ring, the same profile as the gas is used, but with different values for $R_c$ and $\Sigma_c$. The greatest difference is in the outer ring, where we used a decaying power law modulated by the sum of two Gaussian profiles. In an effort to recreate the break seen in the outer ring between 29.8 and 37.9\,au, we chose a different value for $\gamma$ = -3. For the large dust grains the surface density profile is thus
\begin{multline}
  \Sigma_{\mathrm{large-dust}}(r) = \Sigma_{\mathrm{c}2} \left(\frac{r}{R_{\mathrm{c}2}}\right)^{-\gamma} \\ \, \left\{ \exp\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2-\gamma}\right] + \mathrm{exp}\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2}\right]\right\}.
\end{multline}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{allprofiles.png}
        \caption{{\bf Top:} surface density profiles for the gas, the large and small grain populations. {\bf Bottom:} scale height profile $h(r)$. The dashed lines crossing both panels correspond to transition radii in the parametric model.}
    \label{fig:profiles}
\end{figure}

>>>>

Repeating the optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.86$\pm$0.02\,$\degr$, with an inclination of 33.92$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars. We see that both Ring13 and Ring24 both share a very similar orientation and centre, given the errors, and both are offset from the star. %Even though all orientation parameters for Ring13 and Ring24 are consistent within the errors, 
Perhaps due to the joint effect of all these small differences, we can see that there are some hints for a different orientation, as summarised in Fig.~\ref{fig:polarring}.

@@

Assuming a three dimensional model in a cylindrical reference frame with coordinates ($r$, $\theta$, $z$), the gas density ($\rho_{\mathrm{gas}}$) distribution follows
\begin{equation}
  \rho_{\mathrm{gas}}(r,z) =\frac{\Sigma(r) \,\delta(r)}{\sqrt{2\pi} \, H(r)} \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{H(r)}\right)^2\right],
\end{equation}
where $H(r)$ is the scale height profile and $\Sigma(r)$ is the surface density profile. $\Sigma(r)$ is defined by a combination of four individual components: the inner disc, Ring6, Ring13 and Ring24.
\begin{equation}
  \Sigma(r) = \Sigma_{\mathrm{inner\,disc}} + \Sigma_{\mathrm{Ring6}} + \Sigma_{\mathrm{Ring13}} + \Sigma_{\mathrm{Ring24}}
\end{equation}

%$\delta(r)$ parameterises the density drops in the gaps and cavities,

The inner disk follows a power law function defined by
\begin{equation}
  \Sigma_{\mathrm{inner\,disc}}(r) =\Sigma_\mathrm{c} \left(\frac{r}{R_\mathrm{c}}\right)^{-\gamma}  \, \mathrm{exp}\left[-\left(\frac{r}{R_\mathrm{c}}\right)^{2-\gamma}\right],
\end{equation}
where $R_c$ is a characteristic radius and $\gamma$ is the surface density gradient. We used $R_c$ = 16 and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}.

We choose to use a Gaussian profiles to parameterize Ring6 and Ring13,
\begin{equation}
  \Sigma_{\mathrm{Ring}}(r) = \frac{\Sigma_\circ}{\sqrt{2 \pi} \sigma}
  \, \mathrm{exp}\left[-\frac{1}{2}\left(\frac{r-\mu}{\sigma}\right)^{2}\right],
\end{equation}

@@

Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a large inner cavity and scaling factors that account for the larger gap between the rings. For the inner ring, the same profile as the gas is used, but with different values for $R_c$ and $\Sigma_c$. The greatest difference is in the outer ring, where we used a decaying power law modulated by the sum of two Gaussian profiles. In an effort to recreate the break seen in the outer ring between 29.8 and 37.9\,au, we chose a different value for $\gamma$ = -3. For the large dust grains the surface density profile is thus

\begin{equation}
  \Sigma_{\mathrm{large-dust}}(r) = \Sigma_{\mathrm{c}2} \left(\frac{r}{R_{\mathrm{c}2}}\right)^{-\gamma} \exp\left[-\left(\frac{r}{R_{\mathrm{c}2}}\right)^{2-\gamma}\right] .
\end{equation}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{allprofiles.png}
        \caption{{\bf Top:} surface density profiles for the gas, the large and small grain populations. {\bf Bottom:} Aspect ratio profile $h(r)= H(r)/r$. The dashed lines crossing both panels correspond to transition radii in the parametric model.}
    \label{fig:profiles}
\end{figure}
